--- bg:#EEE
title       : Introduction of Food Agriculture Data Browser
subtitle    : Developing Data Products - Course Project
author      : Lan DING
job         : 
framework   :  io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Overview
>- An interactive web data browser for food and agriculture:
 - <https://landing.shinyapps.io/foodagr/>

>- Data Source: [FAOSTAT](http://faostat3.fao.org/download/Q/QC/E)

>- Raw Data:
 - Dimension: 55033 rows, 115 variables
 - Main Variables: `Country`, `County.Code`, `Item`, `Item.Code`, `Element`, `Element.Code`, `Unit`, `Y1961`, `Y1962`...

> - Clean Data:
 - Dimension: 695736 rows, 6 variables
 - Main Variables:`Country, Item`, `Year`, `Area harvested(Ha)`, `Production(tonnes)`, `Yield(Hg/Ha)`

--- .class #id 

## Interface - Pie Chart

- Choose the parameters in sidebar, the top `n` countries will be shown in the pie chart.

- Realised by `googleVis::gvisPieChart`

- Example: top 10 countries in production of wheat


```{r, echo=F,message=F,warning=F,opts.label = 'interactive', results = 'asis'}

library(dplyr)
library(tidyr)
library(googleVis)
source("top.R")

m <- gvisPieChart(top(),options =list(width = 600,height = 400, pieHole=0.5))
#plot(m)
print(m,'chart')

```

---


## Interface - Map 

- Choose the parameters in sidebar, the top `n` countries will be highlighted in the map.

- Realised by `googleVis::gvisGeoChart`

- Example: top 10 countries in production of wheat
```{r, echo=F,message=F,warning=F,results = 'asis'}
source("top.R")

m <- gvisGeoChart(head(top(),10),locationvar="Country",
             colorvar= "Production(tonnes)",
             options=list(width = 600,height = 400,
                          projection="kavrayskiy-vii"))
print(m,'chart')

```

---


## Interface - Motion Chart


- Choose the parameters in the top select-box, you can play with the motion chart.

- Realised by `googleVis::gvisMotionChart`

```{r ,dependson="gv",message=F,results='asis',echo=F}
source("countries.R")

M <- gvisMotionChart(countries(),"Country","Year", options=list(width=600, height=400))
print(M, 'chart')
```


